Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-19 RR_manuscript/Draft_RR.Rmd
🐛 - fix between team var section hard coded values

According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units at 95% credibility.
In other words, the estimated range of variation across teams lies somewhere between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.03 * 1.96) and `r pm(round((meta_bm_prereg_tidy$conf.high[['sd_animal__Intercept']] * 1.96), 2))` (0.07 * 1.96) with 95% credibility.”

@@

The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0)` to `r pm(x = 0.1)` standard units and 95% probability.
The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.
We interpret these values in more details in the Discussion section.

>>>>

According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units at 95% credibility.
In other words, the estimated range of variation across teams lies somewhere between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.03 * 1.96) and `r pm(round((meta_bm_prereg_tidy$conf.high[['sd_animal__Intercept']] * 1.96), 2))` (0.07 * 1.96) standard units with 95% credibility.

@@

The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0)` to `r pm(x = 0.1)` standard units and 95% probability.
The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in segment and word durations that ranges between 7 to 14 ms for segments and between 7 and 33 ms for words at 95% credibility.
We interpret these values in more details in the Discussion section.

### 2023-01-19 RR_manuscript/Draft_RR.tex
🐛 - fix between team var section hard coded values

According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units at 95\% credibility.
In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.13\) (0.07 * 1.96) with 95\% credibility.''

@@

The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.04 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.14 standard units (\(\beta\) = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
We interpret these values in more details in the Discussion section.

>>>>

According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units at 95\% credibility.
In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.13\) (0.07 * 1.96) standard units with 95\% credibility.

@@

The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.04 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.14 standard units (\(\beta\) = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in segment and word durations that ranges between 7 to 14 ms for segments and between 7 and 33 ms for words at 95\% credibility.
We interpret these values in more details in the Discussion section.
